%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CV using kshafayetCV Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,11pt]{article}

\usepackage{kshafayetCV}

\cvtrue

\addbibresource{publications.bib}
\addbibresource{preprints.bib}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header with name and contact information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Name at top of CV
\cvname{Shafayet Khan Shafee}

%-----------------------------------------------------------------
% \contactbar{Email}{Website}{GitHub}
%            {LinkedIn}{Google Scholar URL}
%            {Phone}{Location}
%-----------------------------------------------------------------
\contactbar{sshafee@isrt.ac.bd}{kshafayet.netlify.app}
           {shafayetShafee}{shafayetshafee}
           {https://scholar.google.com/citations?user=GSgDEx0AAAAJ&hl}
           {+880-1791-051104}
           {Dhaka, Bangladesh}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\medskip

Statistician and data scientist with applications in public health and industry.
Committed to methodological rigor, reproducible research, and open-source
software development.

\vspace{-2pt}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Interests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Research Interests}

Causal Inference, Multilevel Modeling, Bayesian Inference, Survival Analysis,
Sensitivity Analysis, Statistical Machine Learning.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Education}

\edublock[
  \item \textbf{Thesis:} Extended the median odds ratio framework for quantifying
        between-cluster variation in hierarchical binary data with more than two
        levels and developed corresponding interval estimators.
  \item \textbf{Selected Coursework:} Causal Inference; Multilevel Modeling;
        Bayesian Inference; Spatial Statistics; Statistical Machine Learning.
]
{M.Sc. in Applied Statistics}
[GPA 3.97 / 4.00]
{Institute of Statistical Research \& Training}
[University of Dhaka]
{Dhaka, Bangladesh}
{2022--2023}

\medskip

\edublock[
  \item \textbf{Project:} Examined the association between caregivers' stimulation
        activities and socio-emotional development in under-five children using
        nationally representative MICS 2019 Bangladesh data and logistic
        regression analysis.
  \item \textbf{Selected Coursework:} Statistical Inference; Multivariate Statistics;
        Generalized Linear Models; Analysis of Time Series; Design of Experiments;
        Epidemiology; Econometrics.
]
{B.Sc. in Applied Statistics}
[CGPA 3.96 / 4.00]
{Institute of Statistical Research \& Training}
[University of Dhaka]
{Dhaka, Bangladesh}
{2018--2022}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Work Experience}

\cvblock[
  \item Applied Bayesian experimental design (Bayes Factor Design Analysis)
        to estimate sample sizes for controlled product rollouts, incorporating
        prior information and evidence-based stopping criteria.
  \item Estimated causal effects of a fintech product rollout on merchant
        transaction behavior using propensity score matching and
        Difference-in-Differences, with explicit attention to covariate balance
        diagnostics.
  \item Used Hierarchical Bayesian modeling to evaluate adoption rates
        across cohorts in a controlled rollout, accounting for small and
        unequal group sizes and propagating uncertainty through to
        product decisions.
  \item Built scalable analytical pipelines using dbt, BigQuery, and cloud
        infrastructure to support reproducible statistical analysis and reporting.
]{Data Scientist}{Dhaka, Bangladesh}{Pathao Pay}{Jan 2025--Present}

\medskip

\cvblock[
  \item Applied causal ML methods---Double ML and generalized random
        forests---to estimate heterogeneous treatment effects across user
        subgroups, connecting industry experimentation practice to the
        causal inference literature.
  \item Co-developed a repayment risk model using Random Survival Forests
        to estimate time-to-repayment distributions, drawing on survival
        analysis methods for a credit risk application.
  \item Designed and analyzed randomized controlled experiments to
        evaluate product initiatives, including cohort construction and
        randomization checks.
]{Data Scientist}{Dhaka, Bangladesh}{Pathao Limited}{Jul 2023--Dec 2024}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifcv
\section*{Publications}

% Define note explaining publication symbols for author annotations
\defbibnote{symbols}{$^\dagger$ Corresponding author \enspace $^*$ Equal contribution}

\nocite{*}
\printbibliography[heading=none, prenote=symbols]
\fi


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Honors & Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Honors \& Awards}

\begin{itemize}
  \awarditem{Dean's Award}
            {Faculty of Science, University of Dhaka}
            {2025}

  \awarditem{Conference Award for Scientists}
            [for the abstract ``Interval Estimation of the Median Odds
            Ratio for Measuring Contextual Effects in Multilevel Data Using a
            Binary Logistic Model'']
            {45th Annual Conference of the International Society for Clinical
            Biostatistics (ISCB45), Thessaloniki, Greece.}
            {2024}

  \awarditem{National Science and Technology (NST) Fellowship}
            [for M.Sc.\ thesis research on multilevel modeling]
            {Ministry of Science and Technology (MoST), Government of Bangladesh}
            {2023}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Talks & Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifcv
\section*{Talks \& Presentations}

\begin{itemize}
  \cvitem{On the Estimation of the Median Odds Ratio for Measuring Contextual
          Effects in Multilevel Binary Data from Complex Survey Designs}
         {International Conference on Applied Statistics and Data Science
          (ICASDS 2025), University of Dhaka}
         {2025}
\end{itemize}
\fi


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifcv
\section*{Technical Skills}

\begin{itemize}[itemsep=2pt, parsep=0pt, topsep=0pt, leftmargin=*]
  \item \textbf{Machine Learning:} Ensemble Models, Causal ML (DML/GRF), Model
        Calibration, Conformal Prediction

  \item \textbf{Data \& MLOps:} BigQuery, dbt, Kedro, MLflow, Docker, Bash.

  \item \textbf{Analytics Tools:} Stata, SPSS, Shiny, Looker Studio, Mixpanel.

  \item \textbf{Programming:} R, Python, Octave, SQL, Lua.

  \item \textbf{Others:} \LaTeX{}, Git, GitHub Actions, GitLab CI.

\end{itemize}

\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Software
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifcv
\section*{Software}

\begin{itemize}
\cvitem{\href{https://github.com/einsteinphysics/relativity-simulator}{\texttt{relativity-simulator}}}{Personal project}{1920-1930}
\cvitem{\href{https://github.com/einsteinphysics/quantum-probability}{\texttt{quantum-probability}}}{Collaborative research}{1924-1935}
\end{itemize}
\fi


\end{document}
