%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CV using kshafayetCV Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt]{article}

\usepackage[type=industry]{kshafayetCV}

\addbibresource{job.bib}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header with name and contact information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Name at top of CV
\cvname{Shafayet Khan Shafee}

%-----------------------------------------------------------------
% \contactbar{Email}{Website}{GitHub}
%            {LinkedIn}{Google Scholar URL}
%            {Phone}{Location}
%-----------------------------------------------------------------
\contactbar{sshafee@isrt.ac.bd}{kshafayet.netlify.app}
           {shafayetShafee}{shafayetshafee}
           {https://scholar.google.com/citations?user=GSgDEx0AAAAJ&hl}
           {+880-1791-051104}
           {Dhaka, Bangladesh}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{5pt}

Data Scientist specializing in experimentation, causal inference, and machine
learning for data-driven decision-making, with experience building analytics
systems and ML solutions in fintech. Experienced in owning the full analytical
lifecycle, from framing ambiguous business problems to delivering measurable
outcomes through experimentation, causal analysis, Bayesian methods, and
predictive modeling, including shipping ML and data pipelines to production.
Interested in applying rigorous statistical thinking to large-scale,
product-led environments, particularly at the intersection of causal inference
and Bayesian methods.

\vspace{-2pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Professional Experience}

\cvblock[

  \item Led the design and execution of 5 end-to-end randomized experiments across
  fintech product and marketing initiatives, spanning both user and merchant
  populations. Translated experiment findings into product and growth decisions
  by identifying actionable interventions, detecting ineffective interventions
  early, and preventing unnecessary promotional spend.

  \item Evaluated the causal impact of a fintech product rollout on merchant
  business outcomes in a non-randomized setting using quasi-experimental
  methods, including propensity score matching, inverse probability weighting,
  and Difference-in-Differences. Generated causal evidence to support rollout
  decisions when randomized experimentation was not feasible.

  \item Improved controlled rollout planning by applying Bayesian experimental
  design to determine sample sizes using probabilistic criteria, making tradeoffs
  between statistical confidence, operational cost, and experiment efficiency
  explicit and communicable to stakeholders.

  \item Evaluated product adoption across small and unequal-sized cohorts using
  hierarchical Bayesian modeling, enabling more reliable estimates under limited
  data by quantifying uncertainty and supporting risk-aware rollout decisions.

  \item Architected and maintained a centralized analytics transformation layer
  using dbt and BigQuery on GCP, converting fragmented raw data sources into
  structured analytical models. Built reusable production datasets that simplified
  downstream analysis, reduced typical query scans from GB-scale to MB-scale,
  lowered BigQuery costs, and standardized metrics across Growth, Product,
  Operations, and Finance analytics teams.

]{Data Scientist}{Dhaka, Bangladesh}{Pathao Pay}{Jan 2025 -- Present}

\medskip

\cvblock[
  \item Designed and owned 2 end-to-end randomized experiments to optimize BNPL
  repayment engagement, testing notification strategies across thousands of users.
  Demonstrated the impact of increased repayment communications in reducing
  post-due unpaid user rate, contributing to a ~4\% reduction after broader rollout without
  negatively impacting monthly active users.

  \item Developed a causal ML-based personalization framework using Double Machine
  Learning and causal forests to estimate heterogeneous treatment effects across
  user subgroups. Enabled targeted promotion strategies by identifying high-response
  segments, contributing to a 35\% reduction in monthly promotional spend while
  maintaining comparable user activity and business performance.

  \item Co-developed a repayment collection prioritization framework using Random
  Survival Forests to estimate time-to-repayment and stratify overdue BNPL users
  by repayment likelihood. Optimized limited CX call capacity by prioritizing
  users with higher likelihood of repayment following outreach while reducing
  unnecessary collection efforts.

  \item Co-developed a credit risk scoring framework for BNPL applicants using
  XGBoost to estimate probability of default. Enabled risk-based user segmentation
  and dynamic credit limit assignment, allowing the business to expand BNPL access
  while managing credit risk exposure.

  \item Built automated reporting workflows using dbt, BigQuery, Looker Studio,
  and Google Apps Script, delivering executive dashboards used by Fintech
  and Finance leadership to monitor key business metrics. Reduced manual
  reporting overhead and improved access to timely business insights.

]{Data Scientist}{Dhaka, Bangladesh}{Pathao Limited}{Jul 2023 -- Dec 2024}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Technical Skills}

\begin{itemize}[itemsep=2pt, parsep=0pt, topsep=0pt, leftmargin=*]

  \item \textbf{Programming Languages:} Python, R, SQL.

  \item \textbf{Machine Learning:} Ensemble Methods, Survival Modeling, Conformal
        Prediction, Model Calibration, Causal ML (DML, Causal Forest, BCF).

  \item \textbf{Statistics:} Hypothesis Testing, Bayesian Modeling,
        Causal Inference (IPW, Matching, DiD), A/B Testing, Time Series Analysis.

  \item \textbf{Data \& ML Engineering:} dbt, Kedro, MLflow, Bash Scripting.

  \item \textbf{Tools \& Platforms:} BigQuery, GCP, Docker, Git,
        CI/CD (GitHub Actions, GitLab CI).

  \item \textbf{Analytics \& Visualization:} Looker Studio, MixPanel, Shiny.

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Education}

\edublock[]{M.Sc. in Applied Statistics}
[GPA 3.97 / 4.00]
{ISRT, University of Dhaka}
[]
{Dhaka, Bangladesh}
{2022--2023}

\medskip

\edublock[]{B.Sc. in Applied Statistics}
[CGPA 3.96 / 4.00]
{ISRT, University of Dhaka}
[]
{Dhaka, Bangladesh}
{2018--2022}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Publications}

\nocite{*}
\printbibliography[heading=none]



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Open Source Contributions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Open Source}

\begin{itemize}[itemsep=2pt, parsep=0pt, topsep=0pt, leftmargin=*]

  \item \href{https://skmiscpy.readthedocs.io}{\texttt{skmiscpy}} --- Python package
        for causal inference diagnostics, including Love plots, mirror histograms,
        and SMD computation for IPW workflows.

  \item \href{https://github.com/shafayetShafee/randomizer}{\texttt{randomizer}} ---
        Dockerized Shiny app for experimental unit randomization with SRM testing
        and covariate balance diagnostics.

  \item \href{https://github.com/shafayetShafee/kedrogen}{\texttt{kedrogen}} ---
        CLI tool for scaffolding reproducible data science projects from
        cookiecutter templates.

  \item \href{https://github.com/shafayetShafee/python-uv-gcloud}{\texttt{python-uv-gcloud}} ---
        Minimal Docker base image with Python, \texttt{uv}, and Google Cloud SDK
        for CI/CD pipelines and cloud workflows.

  \item \href{https://shafayetshafee.github.io/MOR/}{\texttt{MOR}} --- R package
        implementing post-estimation functions to compute the Median Odds Ratio
        and confidence intervals from fitted multilevel binary logistic models.

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Honors & Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Awards \& Achievements}

\begin{itemize}
  \awarditem{Dean's Award}
            {Faculty of Science, University of Dhaka}
            {2025}

  \awarditem{Conference Award for Scientists}
            {45th Annual Conference of the ISCB, Thessaloniki, Greece}
            {2024}

  \awarditem{Datathon Finalist}
            [Top 10 of 300 teams; built a purchase-behavior prediction model for mobile data packages]
            {Robi Axiata Limited, Dhaka, Bangladesh.}
            {2024}

  \awarditem{National Science and Technology (NST) Fellowship}
            [M.Sc.\ thesis research in multilevel modeling]
            {Ministry of Science and Technology (MoST), Government of Bangladesh}
            {2023}
\end{itemize}


\end{document}

